---
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    highlight: "default"
    number_sections: true
    df_print: kable

urlcolor: blue

params:
  report_title: "Title"

mainfont: IBM Plex Sans

header-includes: 
  \usepackage{graphicx}
  \usepackage{fontspec}
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \usepackage{color}
  \usepackage{hyperref}
  \usepackage{longtable}
  \setlength{\LTleft}{2em}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{multirow}
  \usepackage{wrapfig}
  \usepackage{float}
  \usepackage{xcolor}
  \usepackage{pdflscape}
  \usepackage{tabu}
  \usepackage{threeparttable}
  \usepackage{caption}
  \usepackage{makecell}
  \usepackage{multicol}
  \usepackage{lscape}
  \usepackage{eso-pic}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }

---
\definecolor{g6tr_blue}{RGB}{54, 200, 239}
\definecolor{g6tr_green}{RGB}{80, 189, 144}
\definecolor{g6tr_yellow}{RGB}{255, 207, 96}
\definecolor{g6tr_links}{RGB}{0, 120, 205}
\setmonofont[]{IBM Plex Mono}
\hypersetup{
    linkcolor=black,
    urlcolor=g6tr_links
}


\AddToShipoutPicture*{%
 \AtPageUpperLeft{\raisebox{-\height}{\includegraphics[width = \paperwidth]{assets/pdf-gradient.png}}}}

\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\includegraphics[width=0.2\textwidth]{assets/Gradient_Logo_Black.png}}

\fancyfoot{}
\fancyfoot[C]{\texttt{`r params$report_title`}}

\fancyfoot[R]{\textbf{\thepage}}

```{r setup, echo = F, warning = F, message = F}
knitr::opts_chunk$set(echo = F, 
                      eval = T,
                      comment = "", 
                      cache = F,
                      message = F, 
                      warning = F,
                      fig.align = "center",
                      fig.height = 4,
                      fig.width = 8,
                      strip.white = TRUE,
                      size = '14',
                      background = "#FFFFFF",
                      results = "asis",
                      out.width = "7.3in"
                      )

```

```{r child = '001_title.Rmd'}
```

```{r child = '002_libraries.Rmd'}
```

```{r child = '003_data.Rmd', cache = T}
```

```{r child = '100_intro.Rmd'}
```
\newpage
```{r child = '200_section.Rmd'}
```
\newpage
```{r child = '300_section.Rmd'}
```
